Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-09-28 Docs/TODAES/paper.tex
final reviews

The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}. Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost. In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values. \textit{Fobj} should be minimized to obtain the optimal hardware solution. To achieve this, two constraints are imposed to $\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to $\nu$Z that \textit{Fobj} should be minimized. Finally, the model is checked by $\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.

\begin{lstlisting}[caption=Pseudocode describing $\nu$Z.,label=vZ-pseudocode, mathescape]
#Initialize Variables
  Create vZ context 
  Create binary vector (x)
  Declare number of nodes, edges and $S_{0}$
  Declare hardware cost of each node as array (h) 
  Declare software cost of each node as array (s)
  Declare communication cost of each edge (c)
  Declare transposed incidence matrix graph G (E)
#Arithmetic Expressions
  SC = s(1-x)
  CMC = c*|EX|
  Fobj =  x[i] * h[i]
#Assert Constraints
  Add constraints (SF + CMC <= $S_{0}$)
  Add constraints to minimize Fobj
  Check Model
  Print Result
\end{lstlisting}

@@

This section is split into three parts. The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation. Section~\ref{Experimental-Results} reports a comparison among Matlab~\cite{TheMathWorks2013}, Multi-Core ESBMC, and MaxSMT $\nu$Z~\cite{Bjorner2015} using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.

@@

ESBMC $1$.$24$ running on a $64$-bit Ubuntu $14$.$04$.$1$ LTS operating system was used. A parallel approach of the ESBMC-SS, ESBMC-PS, ESBMC-PB were implemented in C$++$11. Version $2$.$0$.$1$ of Boolector SMT-solver~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC. For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used~\cite{TheMathWorks2013}. MATLAB is a dynamically typed high-level language, known as the state-of-the-art mathematical software~\cite{Tranquillo2011} and is widely used by the engineering community~\cite{Hong2010}. ESBMC-$\nu$Z as a built-in tool to Z3 was also used~\cite{Bjorner2014}.

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $XX$\% to ESBMC, $92$\% to $\nu$Z, and $YY$\% to ILP. A time out condition (TO) is reached when the verification time is longer than $7200$ seconds. A memory out (MO) occurs when the tool reaches $24$GB of memory.

>>>>

The arithmetic expressions from lines $10$ to $12$ represent the constraints described in Eq.~\ref{hw-sw-partitioning}. Here, variable \textit{SC} refers to the software cost, while \textit{CC} denotes the communication cost. In line $12$, the \textit{Fobj} (objective function) is declared, which denotes the product between the hardware cost and the decision variables vector, which contains only Boolean values. \textit{Fobj} should be minimized to obtain the optimal hardware solution. To achieve this, two constraints are imposed to ESBMC-$\nu$Z: the first one refers to the sum of the software and communication costs, where the result should be less than $S_0$; and the second one informs to ESBMC-$\nu$Z that \textit{Fobj} should be minimized. Finally, the model is checked by ESBMC-$\nu$Z and if there is a solution that meets the constraints, then the \textit{Fobj} value is provided.

\begin{lstlisting}[caption=Pseudocode describing ESBMC-$\nu$Z.,label=vZ-pseudocode, mathescape]
#Initialize Variables
  Create vZ context 
  Create binary vector (x)
  Declare number of nodes, edges and $S_{0}$
  Declare hardware cost of each node as array (h) 
  Declare software cost of each node as array (s)
  Declare communication cost of each edge (c)
  Declare transposed incidence matrix graph G (E)
#Arithmetic Expressions
  SC = s(1-x)
  CMC = c*|EX|
  Fobj =  x[i] * h[i]
#Assert Constraints
  Add constraints (SF + CMC <= $S_{0}$)
  Add constraints to minimize Fobj
  Check Model
  Print Result
\end{lstlisting}

@@

This section is split into three parts. The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation. Section~\ref{Experimental-Results} reports a comparison among Matlab~\cite{TheMathWorks2013}, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks~\cite{Mann2007}.

@@

ESBMC $1$.$24$ running on a $64$-bit Ubuntu $14$.$04$.$1$ LTS operating system was used. A parallel approach of the ESBMC-SS, ESBMC-PS, ESBMC-PB were implemented in C$++$11. Version $2$.$0$.$1$ of Boolector SMT-solver~\cite{Brummayer2009} (freely available) was used as the default solver for ESBMC. ESBMC-$\nu$Z as a built-in tool to Z3 was also used~\cite{Bjorner2014}.  For ILP and GA formulations, MATLAB R$2013$a from MathWorks with Parallel Computing Toolbox was used~\cite{TheMathWorks2013}. MATLAB is a dynamically typed high-level language, known as the state-of-the-art mathematical software~\cite{Tranquillo2011} and is widely used by the engineering community~\cite{Hong2010}.

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). \textcolor{red}{Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $XX$\% to ESBMC, $92$\% to $\nu$Z, and $YY$\% to ILP}. A time out condition (TO) is reached when the verification time is longer than $7200$ seconds. A memory out (MO) occurs when the tool reaches $24$GB of memory.
